---
title: "Compare MPT Analysis Approaches"
author: "Marius Barth"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Compare MPT Analysis Approaches}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE
  , comment = "#>"
  , warning = FALSE
  , message = FALSE
  , fig.width = 8
)
```

# Prerequisites

First of all, make sure that you have installed the *latest* version of all necessary `R` packages *and* of `JAGS`.
To install `JAGS`, go to [mcmc-jags.sourceforge.net](http://mcmc-jags.sourceforge.net/) and follow installation instructions.
After that, install or update the required R packages:

```{r update-packages, eval = FALSE}
install.packages("MPTmultiverse")
update.packages(ask = FALSE)
```


## Example 1: Bayen & Kuhlmann (2011)

```{r model-and-data}
# load packages
library("MPTmultiverse")

# If you're running the analysis from an .rmd file, you only need to ensure that
# the .rmd, .eqn, and .csv files are all in the same directory.

# ------------------------------------------------------------------------------
# MPT model definition & data

EQN_FILE <- "2HTSM_Submodel4.eqn"
DATA_FILE <- "Kuhlmann_dl7.csv"


# if .csv format uses semicolons ";" (German format):
data <- read.csv2(DATA_FILE, fileEncoding = "UTF-8-BOM")

# if .csv format uses commata "," (international format):
# data <- read.csv(DATA_FILE, fileEncoding = "UTF-8-BOM")

# take a glimpse at the data
head(data)
TreeBUGS::plotFreq(data, boxplot = FALSE, eqn = EQN_FILE)

COL_ID <- "Subject"         # name of the variable encoding subject ID
COL_CONDITION <- "ExpCond"  # name of the variable encoding group membership


# Experimental conditions should be labeled in a meaningful way. To accomplish
# this, you may want to use the `factor` function:
unique(data[, COL_CONDITION])

data[[COL_CONDITION]] <- factor(
  data[[COL_CONDITION]]
  , levels = c(1:2)
  , labels = c("no_load", "load")
)

### check input data frame
head(data)
```

### Options

Every time the package `MPTmultiverse` is loaded, it automatically sets some more
or less useful defaults for model estimation, usage of multiple processor cores,
number of posterior predictive samples, etc.
By calling `mpt_options()` without any parameters, you can inspect these default values.
If you want to change them, call `mpt_options` with the respective parameter specified, i.e. `mpt_options(n.iter = 1000)`.
For testing purposes, you can also specify `mpt_options("test")`, which is a shorthand for setting fast, but highly unreliable settings.
You can set options to defaults, again, by typing the shorthand `mpt_options("default")`.

```{r options, results = 'hide'}
# How to change a single option:
mpt_options(n.iter = 1e3)

# For testing purposes, you can use this shorthand to set fast, but unreliable options:
mpt_options("test")

# List all options that were set for the different analysis approaches:
mpt_options()
```

### Estimation

In the next chunk, the main computations are done.
Type `?fit_mpt` in the R console if you want to find out more about the parameters of the function.

```{r echo = FALSE}
set.seed(42)
mpt_options("default")
```

```{r analysis, results = 'hide', eval = FALSE}
results <- fit_mpt(
  model = EQN_FILE
  , dataset = DATA_FILE
  , data = data
  , id = COL_ID
  , condition = COL_CONDITION
  , core = c("D", "d")
)
```

```{r echo = FALSE}
save(results, file = "../inst/extdata/results_bayen_kuhlmann.RData")
```


### Post-processing of Results

```{r results, eval = FALSE}
# convergence results
check_results(results)

# store results
save(
  results
  , file = "results_bayen_kuhlmann.RData"
)
```

The analysis output `results` is an object of class `multiverseMPT`, that has its own `plot()` method.
Type `?plot.multiverseMPT` to see the documentation of possible arguments to this method.

To plot group-level parameter estimates, type:

```{r}
plot(results, save = FALSE, "est")
```

To plot between-subjects comparisons, type:

```{r}
plot(results, save = FALSE, "test_between")
```

To plot overall goodness-of-fit, type:

```{r}
plot(results, save = FALSE, "gof1")
```

To plot group-wise goodness-of-fit, type:

```{r}
plot(results, save = FALSE, "gof2")
```



