---
title: "Compare MPT Analysis Approaches"
author: "Marius Barth"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Compare MPT Analysis Approaches}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE
  , comment = "#>"
  , warning = FALSE
  , message = FALSE
)
```

# Prerequisites

First of all, make sure that you have installed the *latest* version of all necessary `R` packages *and* of `JAGS`.
To install `JAGS`, go to [mcmc-jags.sourceforge.net](http://mcmc-jags.sourceforge.net/) and follow installation instructions.
After that, install or update the required R packages:

```{r install-packages, eval = FALSE}
required <- c(
  "devtools"
  , "tidyr"
  , "dplyr"
  , "tibble"
  , "rlang"
  , "reshape2"
  , "ggplot2"
  , "MPTinR"
  , "TreeBUGS"
  , "runjags"
  , "purrr"
  , "readr"
  , "broom"
)

install.packages(required, repos = "https://cloud.r-project.org")
devtools::install_github("mariusbarth/MPTmultiverse")
```



## Example 1: Bayen & Kuhlmann (2011)

```{r model-and-data}
# load packages:
library("MPTmultiverse")


# Make sure that working directory is correct via either:
# - setwd() / getwd()
# - Rstudio->Sessions->Set Working Directory->'To Source File Location'

# If you're running the analysis from an .rmd file, you only need to ensure that
# the .rmd, .eqn, and .csv files are all in the same directory.


# ------------------------------------------------------------------------------
# MPT model definition & Data

EQN_FILE <- "2HTSM_Submodel4.eqn"
DATA_FILE <- "Kuhlmann_dl7.csv"  


### if .csv format uses semicolons ";" (German format):
data <- read.csv2(DATA_FILE, fileEncoding = "UTF-8-BOM")
### if .csv format uses commata "," (international format):
# data <- read.csv(DATA_FILE, fileEncoding = "UTF-8-BOM")

head(data)
TreeBUGS::plotFreq(data, boxplot = FALSE, eqn = EQN_FILE)

COL_ID <- "Subject"         # name of the variable encoding subject ID
COL_CONDITION <- "ExpCond"  # name of the variable encoding group membership

# NOTE: experimental condition should be labeled meaningfully!
unique(data[, COL_CONDITION])

data[[COL_CONDITION]] <- factor(
  data[[COL_CONDITION]]
  , levels = c(1:2)
  , labels = c("no_load", "load")
)

### check input data frame
head(data)
```

### Options

Every time the package `MPTmultiverse` is loaded, it automatically sets some more or less useful defaults for model estimation,
usage of multiple processor cores, number of posterior predictive samples, etc.
By calling `mpt_options()` without any parameters, you can inspect these default values.
If you want to change them, call `mpt_options` with the respective parameter specified, i.e. `mpt_options(n.iter = 1000)`.
For testing purposes, you can also specify `mpt_options("test")`, which is a shorthand for setting fast, but highly unreliable settings.
You can set options to defaults, again, by typing the shorthand `mpt_options("default")`.

```{r options, results = 'hide'}
# How to change a single option:
# mpt_options(n.iter = 1000)

# For testing purposes, you can use this shorthand to set fast, but unreliable options:
mpt_options("test")

# List all options that were set for the different analysis approaches:
# mpt_options()
```

### Estimation

In the next chunk, the main computations are done.
Type `?fit_mpt` in the R console if you want to find out more about the parameters of the function.

```{r analysis, results = 'hide', eval = FALSE}
all_supported_methods <- c(
  "asymptotic_complete"
  , "asymptotic_no"
  , "pb_no"
  , "latent_class"
  , "simple"
  , "simple_pooling"
  , "trait"
  , "trait_uncorrelated"
  , "beta"
)
data$junk <- NA_complex_
results <- fit_mpt(
  method = all_supported_methods
  , dataset = DATA_FILE
  , data = data
  , model = EQN_FILE
  , id = COL_ID
  , condition = COL_CONDITION
)
```


### Post-processing of Results

```{r results, eval = FALSE}
# print convergence results
checks <- (check_results(results))

used_options <- getOption("MPTmultiverse")
# store results
save(
  results
  , data
  , EQN_FILE
  , DATA_FILE
  , used_options
  , checks
  , file = "results.RData"
)

# Write model checks to a file:
# write_check_results(paste0(EQN_FILE, "-", DATA_FILE), results)
```

The analysis output `results` is an object of class `multiverseMPT`, that has its own `plot()` method.
Type `?plot.multiverseMPT` to see the documentation of possible arguments to this method.

```{r eval = FALSE}
plot(results, save = FALSE, "est")
```


```{r eval = FALSE}
plot(results, save = FALSE, "test_between")
```


```{r eval = FALSE}
plot(results, save = FALSE, "gof1")
```

```{r eval = FALSE}
plot(results, save = FALSE, "gof2")
```



